Notes on two photon scattering of the molecular state

### 2019-11-24 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] add \mbox to avoid line break in the middle of figure reference

See figure \ref{two-up-1}A, the loss mechanism we suspect is a two photon coupling
to a lossy continuum with a frequency dependent loss rate
\footnote{The loss rate depends on the laser power, i.e. $\Omega_1$ and $\Omega_2$. Here
  ``loss rate'' essentially mean the loss rate per power squared, which is proportional to
  the square of the coupling from $|e\rangle$ and the density of state.
  Also note here since the second beam is coupling to a continuum rather than a single state
  in the generic case, $\Omega_2$ is not a single number but a function of frequency
  depending of the selection of normalization of the continuum.}.
Generically, the loss rate is not flat which may give us a frequency dependent
two photon loss rate. One way to see the difference between a detuned measurement
and a on-resonance (with the singe photon excited state $|e\rangle$)
measurement of the two photon decay rate is that the two process does not have the same
two photon frequencies. For the on-resonance measurement using the same laser that couples
$|e\rangle$ to the higher excited state (figure \ref{two-up-1}B),
the loss rate experienced by the two photon resonance can be different.
Since the loss rate can have an arbitrary dependency on frequency, one shouldn't expect
the difference in the loss rate to be included in the detuning factor when calculating
the scattering in the off-resonance case.\\

@@

See figure \ref{two-up-2}. The ground state $|g\rangle$ is coupled to $|e_1\rangle$,
$|e_1\rangle$ is coupled to $|e_2\rangle$ and $|e_2\rangle$ can decay to another ground
state $|g'\rangle$ with decay rate $\Gamma$ and a $100\%$ branching ratio.
The energy of the two ground states $|g\rangle$ and $|g'\rangle$ are both $0$,
the energy of $|e_1\rangle$ is $\omega_0$ and the energy of $|e_2\rangle$ is $\omega_0+\omega$.\\

@@

See figure \ref{two-up-coupled}A. The excited states becomes

@@

Let the $D_1=\langle g|\hat d|e_1\rangle$ and $D_2=\langle g'|\hat d|e_2\rangle$ be
the dipole moment coupling $e_1$ and $e_2$ to the corresponding ground states $g$ and $g'$.
The dipole moments between the new states are shown in figure \ref{two-up-coupled}B
\footnote{The sign of the dipole moment depends on the selection of the phase for
  $|\pm\rangle$ but the relative sign of the product does not depend on the phase selection}.\\

>>>>

See \mbox{figure \ref{two-up-1}A}, the loss mechanism we suspect is a two photon coupling
to a lossy continuum with a frequency dependent loss rate
\footnote{The loss rate depends on the laser power, i.e. $\Omega_1$ and $\Omega_2$. Here
  ``loss rate'' essentially mean the loss rate per power squared, which is proportional to
  the square of the coupling from $|e\rangle$ and the density of state.
  Also note here since the second beam is coupling to a continuum rather than a single state
  in the generic case, $\Omega_2$ is not a single number but a function of frequency
  depending of the selection of normalization of the continuum.}.
Generically, the loss rate is not flat which may give us a frequency dependent
two photon loss rate. One way to see the difference between a detuned measurement
and a on-resonance (with the singe photon excited state $|e\rangle$)
measurement of the two photon decay rate is that the two process does not have the same
two photon frequencies. For the on-resonance measurement using the same laser that couples
$|e\rangle$ to the higher excited state (\mbox{figure \ref{two-up-1}B}),
the loss rate experienced by the two photon resonance can be different.
Since the loss rate can have an arbitrary dependency on frequency, one shouldn't expect
the difference in the loss rate to be included in the detuning factor when calculating
the scattering in the off-resonance case.\\

@@

See \mbox{figure \ref{two-up-2}}. The ground state $|g\rangle$ is coupled to $|e_1\rangle$,
$|e_1\rangle$ is coupled to $|e_2\rangle$ and $|e_2\rangle$ can decay to another ground
state $|g'\rangle$ with decay rate $\Gamma$ and a $100\%$ branching ratio.
The energy of the two ground states $|g\rangle$ and $|g'\rangle$ are both $0$,
the energy of $|e_1\rangle$ is $\omega_0$ and the energy of $|e_2\rangle$ is $\omega_0+\omega$.\\

@@

See \mbox{figure \ref{two-up-coupled}A}. The excited states becomes

@@

Let the $D_1=\langle g|\hat d|e_1\rangle$ and $D_2=\langle g'|\hat d|e_2\rangle$ be
the dipole moment coupling $e_1$ and $e_2$ to the corresponding ground states $g$ and $g'$.
The dipole moments between the new states are shown in \mbox{figure \ref{two-up-coupled}B
\footnote{The sign of the dipole moment depends on the selection of the phase for
  $|\pm\rangle$ but the relative sign of the product does not depend on the phase selection}.}\\
